---
title: "How are the snippets produced?"
author: "Liolia Bajemon"
format: html
editor: visual
---

### Description

The aim of this document is to generate plots illustrating the way snippets are produced for a few study cases.

We already have tables containing SERP results, resulting from multiple queries of the type "river and city". It is assumed that snippets, which appear in SERP, correspond to short extracts of a given website. To verify this hypothesis, it is necessary to check manually whether snippets are truly extracts from websites or made otherwise, *e.g.* by AI. We selected a few cities (n = XXX) and verified this hypothesis for each snippet (m = 100). We came up with diverse explanations:

-   The snippet corresponds to the 1st sentence of the page;

-   The snippet is an extract from the page, but not the 1st sentence;

-   The snippet has been suggested in the metadata of the website ("description"). This has been found by doing a right click on the page and displaying its source code;

-   The snippet comes from another page, which is related to this page thanks to a hyperlink;

-   The source of the snippet is unknown;

-   There is no snippet.

### Set-up

First, let's retrieve our data and load some packages.

```{r set_up}
library(tidyverse)
```

#### Calculation of the number of occurrences

```{r n_occ}
n_occ = function(df){
  df = df %>% 
    # replace NA values    
    mutate(snippet_from = replace_na(snippet_from, "Pas de snippet")) %>% 
    # put everything in lower case
    mutate(snippet_from = str_to_lower(snippet_from)) %>% 
    group_by(snippet_from) %>%  
    count(snippet_from)
}
```

```{r plot}
plot_snip = function(df, fichier, nb_snip, soustitre){
   
  # rearrange df by decreasing order
  df$snippet_from = with(df, reorder(snippet_from, n))
  
  plot = df %>% 
    ggplot(mapping = aes(x = snippet_from,
                         y = n)) +
    geom_col(position = "stack", fill = "#8dd3c7") +
    coord_flip() + # flip x and y coordinates 
    labs(title = paste0("Origine des snippets (n = ", nb_snip,")"), 
         subtitle = soustitre,
         x = "",
         y = "nombre de snippets",
         caption = "L. Bajemon, juillet 2024") +
    theme_bw() +
    theme(legend.position = "right",
          plot.caption.position = "plot")
    
  ggsave(filename = fichier, plot = plot, width = 7, height = 5, units = "in")
}
```

#### Types of websites

```{r n_typo}
n_typo = function(df){
  df = df %>% 
    # group by value
    group_by(type) %>%  
    # count number of values for each group
    count(type)
  }
```

```{r plot_typo}
plot_typo = function(df, fichier, nb_snip, soustitre){
   
  # rearrange df by decreasing order
  df$type = with(df, reorder(type, n))
  
  plot = df %>% 
    ggplot(mapping = aes(x = type,
                         y = n)) +
    geom_col(position = "stack", fill = "#b3de69") +
    labs(title = paste0("Types de sites Internet (n = ", nb_snip,")"), 
         subtitle = soustitre, 
         x = "",
         y = "nombre de sites",
         caption = "L. Bajemon, juillet 2024") +
    coord_flip() + # flip x and y coordinates 
    theme_bw() +
    theme(legend.position = "right",
          plot.caption.position = "plot") 
  
  ggsave(filename = fichier, plot = plot, width = 7, height = 5, units = "in")
}
```

### Run functions

```{r run}
# run functions for origin of snippets
plot_snip(n_occ(read.csv("analysis/critical/lyon_rhone_EN.csv")), "analysis/critical/snippets_from_lyon_en.png", nrow(read.csv("analysis/critical/lyon_rhone_EN.csv")), "Requête en anglais : Rhône river and Lyon")
plot_snip(n_occ(read.csv("analysis/critical/lyon_rhone_FR.csv")), "analysis/critical/snippets_from_lyon_fr.png", nrow(read.csv("analysis/critical/lyon_rhone_FR.csv")), "Requête en français : fleuve Rhône et Lyon")
plot_snip(n_occ(read.csv("analysis/critical/montreal_st-laurent_FR.csv")), "analysis/critical/snippets_from_montreal_fr.png", nrow(read.csv("analysis/critical/montreal_st-laurent_FR.csv")), "Requête en français : fleuve Saint-Laurent et Montréal")
plot_snip(n_occ(read.csv("analysis/critical/montreal_st-laurent_EN.csv")), "analysis/critical/snippets_from_montreal_en.png", nrow(read.csv("analysis/critical/montreal_st-laurent_EN.csv")), "Requête en anglais : Saint Lawrence river and Montréal")
plot_snip(n_occ(read.csv("analysis/critical/ahmedabad_sabarmati_EN.csv")), "analysis/critical/snippets_from_ahmedabad_en.png", nrow(read.csv("analysis/critical/ahmedabad_sabarmati_EN.csv")), "Requête en anglais : Sabarmati river and Ahmedabad")
plot_snip(n_occ(read.csv("analysis/critical/ahmedabad_sabarmati_HI.csv")), "analysis/critical/snippets_from_ahmedabad_hi.png", nrow(read.csv("analysis/critical/ahmedabad_sabarmati_HI.csv")), "Requête en hindi (fleuve Sabarmati et Ahmedabad)")
plot_snip(n_occ(read.csv("analysis/critical/denver_south-platte_en.csv")), "analysis/critical/snippets_from_denver_en.png", nrow(read.csv("analysis/critical/denver_south-platte_en.csv")), "Requête en anglais : South Platte river and Denver")
plot_snip(n_occ(read.csv("analysis/critical/abomey-calavi_oueme_EN.csv")), "analysis/critical/snippets_from_abomey_en.png", nrow(read.csv("analysis/critical/abomey-calavi_oueme_EN.csv")), "Requête en anglais : Ouémé river and Abomey-Calavi")
plot_snip(n_occ(read.csv("analysis/critical/abomey-calavi_oueme_FR.csv")), "analysis/critical/snippets_from_abomey_fr.png", nrow(read.csv("analysis/critical/abomey-calavi_oueme_FR.csv")), "Requête en français : fleuve Ouémé et Abomey-Calavi")
plot_snip(n_occ(read.csv("analysis/critical/ufa_belaya_EN.csv")), "analysis/critical/snippets_from_ufa_en.png", nrow(read.csv("analysis/critical/ufa_belaya_EN.csv")), "Requête en anglais : Belaya river and Ufa")
plot_snip(n_occ(read.csv("analysis/critical/ufa_belaya_RU.csv")), "analysis/critical/snippets_from_ufa_ru.png", nrow(read.csv("analysis/critical/ufa_belaya_RU.csv")), "Requête en russe : rivière Belaya et Ufa")


# run functions for types of websites
plot_typo(n_typo(read.csv("analysis/critical/lyon_rhone_EN.csv")), "analysis/critical/typologie_lyon_en.png", nrow(read.csv("analysis/critical/lyon_rhone_EN.csv")), "Requête en anglais : Rhône river and Lyon")
plot_typo(n_typo(read.csv("analysis/critical/lyon_rhone_FR.csv")), "analysis/critical/typologie_lyon_fr.png", nrow(read.csv("analysis/critical/lyon_rhone_FR.csv")), "Requête en français : fleuve Rhône et Lyon")
plot_typo(n_typo(read.csv("analysis/critical/montreal_st-laurent_FR.csv")), "analysis/critical/typologie_montreal_fr.png", nrow(read.csv("analysis/critical/montreal_st-laurent_FR.csv")), "Requête en français : fleuve Saint-Laurent et Montréal")
plot_typo(n_typo(read.csv("analysis/critical/montreal_st-laurent_EN.csv")), "analysis/critical/typologie_montreal_en.png", nrow(read.csv("analysis/critical/montreal_st-laurent_EN.csv")), "Requête en anglais : Saint Lawrence river and Montreal")
plot_typo(n_typo(read.csv("analysis/critical/ahmedabad_sabarmati_EN.csv")), "analysis/critical/typologie_ahmedabad_en.png", nrow(read.csv("analysis/critical/ahmedabad_sabarmati_EN.csv")), "Requête en anglais : Sabarmati river and Ahmedabad")
plot_typo(n_typo(read.csv("analysis/critical/ahmedabad_sabarmati_HI.csv")), "analysis/critical/typologie_ahmedabad_hi.png", nrow(read.csv("analysis/critical/ahmedabad_sabarmati_HI.csv")), "Requête en hindi (fleuve Sabarmati et Ahmedabad)")
plot_typo(n_typo(read.csv("analysis/critical/denver_south-platte_en.csv")), "analysis/critical/typologie_denver_en.png", nrow(read.csv("analysis/critical/denver_south-platte_en.csv")), "Requête en anglais : South Platte river and Denver")
plot_typo(n_typo(read.csv("analysis/critical/abomey-calavi_oueme_EN.csv")), "analysis/critical/typologie_abomey_en.png", nrow(read.csv("analysis/critical/abomey-calavi_oueme_EN.csv")), "Requête en anglais : Ouémé river and Abomey-Calavi")
plot_typo(n_typo(read.csv("analysis/critical/abomey-calavi_oueme_FR.csv")), "analysis/critical/typologie_abomey_fr.png", nrow(read.csv("analysis/critical/abomey-calavi_oueme_FR.csv")), "Requête en français : fleuve Ouémé et Abomey-Calavi")
plot_typo(n_typo(read.csv("analysis/critical/ufa_belaya_RU.csv")), "analysis/critical/typologie_ufa_ru.png", nrow(read.csv("analysis/critical/ufa_belaya_RU.csv")), "Requête en russe : rivière Belaya et Ufa")
plot_typo(n_typo(read.csv("analysis/critical/ufa_belaya_EN.csv")), "analysis/critical/typologie_ufa_en.png", nrow(read.csv("analysis/critical/ufa_belaya_EN.csv")), "Requête en anglais : Belaya river and Ufa")
```

### Bind everything

```{r read_data}
df1 = read.csv("analysis/etude_10_villes/lyon_rhone_EN.csv") %>%
  select("snippet_from") 
df3 = read.csv("analysis/etude_10_villes/abomey-calavi_oueme_EN.csv") %>%
    select("snippet_from")
df4 = read.csv("analysis/etude_10_villes/abomey-calavi_oueme_FR.csv") %>%
    select("snippet_from")
df5 = read.csv("analysis/etude_10_villes/ahmedabad_sabarmati_EN.csv") %>%
    select("snippet_from")
df6 = read.csv("analysis/etude_10_villes/ahmedabad_sabarmati_HI.csv") %>%
    select("snippet_from")
df7 = read.csv("analysis/etude_10_villes/denver_south-platte_EN.csv") %>%
    select("snippet_from")
df8 = read.csv("analysis/etude_10_villes/montreal_st-laurent_EN.csv") %>%
    select("snippet_from")
df9 = read.csv("analysis/etude_10_villes/montreal_st-laurent_FR.csv") %>%
    select("snippet_from")
df10 = read.csv("analysis/etude_10_villes/ndjamena_chari_EN.csv") %>%
    select("snippet_from")
df11 = read.csv("analysis/etude_10_villes/ndjamena_chari_FR.csv") %>%
    select("snippet_from")
df12 = read.csv("analysis/etude_10_villes/ndjamena_chari_AR.csv") %>%
    select("snippet_from")
df13 = read.csv("analysis/etude_10_villes/nha_trang_cai_EN.csv") %>%
    select("snippet_from")
df14 = read.csv("analysis/etude_10_villes/nha_trang_cai_VI.csv") %>%
    select("snippet_from")
df15 = read.csv("analysis/etude_10_villes/ufa_belaya_EN.csv") %>%
    select("snippet_from")
df16 = read.csv("analysis/etude_10_villes/ufa_belaya_RU.csv") %>%
    select("snippet_from")
df17 = read.csv("analysis/etude_10_villes/wuhan_yangtze_EN.csv") %>%
    select("snippet_from")
df18 = read.csv("analysis/etude_10_villes/wuhan_yangtze_ZH.csv") %>%
    select("snippet_from")
df19 = read.csv("analysis/etude_10_villes/xuanwei_beipan_EN.csv") %>%
    select("snippet_from")
df20 = read.csv("analysis/etude_10_villes/xuanwei_beipan_ZH.csv") %>%
    select("snippet_from")

df = df1 %>% 
  rbind(df3) %>% 
  rbind(df4) %>% 
  rbind(df5) %>% 
  rbind(df6) %>%   
  rbind(df7) %>% 
  rbind(df8) %>%   
  rbind(df9) %>% 
  rbind(df10) %>%   
  rbind(df11) %>% 
  rbind(df12) %>%   
  rbind(df13) %>% 
  rbind(df14) %>% 
  rbind(df15) %>%
  rbind(df16) %>%  
  rbind(df17) %>%  
  rbind(df18) %>%
  rbind(df19) %>%
  rbind(df20)
```

Plot everything:

```{r}
## PLOT
data = df %>%
  filter(snippet_from != "") %>% 
  mutate(snippet_from = gsub("^\\s+|\\s+$", "", snippet_from)) %>% 
  group_by(snippet_from) %>% 
  count() %>% 
  mutate(perc = n/sum(data$n)*100) %>% 
  mutate(n = as.numeric(n)) 
# ca veut pas se trier dans l'ordre donc je le fais à la main sur excel 
write.csv(data, "analysis/etude_10_villes/compilation_snippets_from.csv", row.names = FALSE)
data_sorted = read.csv("analysis/etude_10_villes/compilation_snippets_from.csv")

  data_sorted %>% 
    mutate(snippet_from = forcats::fct_reorder(snippet_from, perc)) %>% 
    ggplot(mapping = aes(x = snippet_from,
                         y = perc)) +
    geom_col(position = "stack", fill = "#b3de69") +
    coord_flip() + # flip x and y coordinates 
    labs(x = "",
         y = "%") +
    theme_light() +
    theme(legend.position = "right",
          plot.caption.position = "plot")
    
  ggsave(filename = "analysis/etude_10_villes/provenance_snippets.png", width = 7, height = 3, units = "in")
```
